
```{r}
#library a bunch of packages we may (or may not) use - install them first if not installed already. 
library(tidyverse)
library(tmap)
library(geojsonio)
library(plotly)
library(broom)
library(mapview)
library(sf)
library(sp)
library(spdep)
library(car)
library(fs)
library(janitor)
library(gstat)
library(raster)
library(MASS)
```


```{r}
#read in some attribute data
LSOA_M <- st_read(here::here("Manchester.shp"))

```

```{r}
LSOA_M<- rename(LSOA_M, Mean_price = Mean.pri15)
```


```{r}
LSOA_M<- subset(LSOA_M, select= -c(Mean.pri_1, Mean.pri_2, Mean.pri_3, Mean.pri_4, Mean.pri_5, Mean.pri_6, Mean.pri_7,
            Mean.pri_8, Mean.pri_9, Mean.pri10, Mean.pri11, Mean.pri12, Mean.pri13, Mean.pri14))
```

```{r}
LSOA_M<- subset(LSOA_M, select= -c(Column2,OutputAr_1,Column2_2,Mean.price))
```


#Kriging：Mean price 2021 Manchester  （1.5min）
```{r}

kriging_model_M <- gstat(formula = Mean ~ 1, data = na.omit(LSOA_M), model = vgm(1, "Sph", 900, 1))


kriging_result_M <- predict(kriging_model_M, newdata = LSOA_M)

```
#The interpolated mean price 2021 has the column name var1.pred and then merged into shapefile:LSOA_B called: mean_price_filled_M

```{r}

LSOA_M$Mean_price_M <- kriging_result_M$var1.pred

head(LSOA_M)
```

```{r}
print(kriging_result_M)

```


## Census variable join

```{r}

 Manchester_census <- read_csv("manchester_census_new.csv")
```

```{r}

 Manchester_census <- read_csv("manchester_census_new.csv")
```

```{r}

Manchester_edu <- read_csv("manchest_edu.csv")
```


```{r}

LSOA_M <- left_join(LSOA_M, , by = c("OutputArea" = "OutputArea"))

```

```{r}

LSOA_M <- left_join(LSOA_M, Manchester_census, by = c("OutputArea" = "OutputArea"))

```

# house prices join
```{r}

house_price <- read_csv("Mean price_EDITED.csv")
```


```{r}

LSOA_M <- left_join(LSOA_M, house_price, by = c("OutputArea" = "LSOA code"))

```

```{r}

modelM_full <- lm(Mean_price_M ~ population + bedrooms_4more + bedrooms_2 + bedrooms_3 +
            workdistance_home + workdistance_10to30 + workdistance_30more + workdistance_outside
            +centralheating_no+cars_no+cars_2+cars_3more
            +edu_apprenticeship+edu_level_4more+edu_other+edu_level_1to3
            +workstatus_ft+workstatus_pt+workstatus_retired+workstatus_other, 
            data = LSOA_M)
summary(modelM_full)
```

```{r}

modelM_full <- lm(Mean_price_M ~ population + bedrooms_4more + bedrooms_2 + bedrooms_3 +
            workdistance_home + workdistance_10to30 + workdistance_30more + workdistance_outside
            +centralheating_no+cars_no+cars_2+cars_3more
            +edu_apprenticeship+edu_level_4more+edu_other+edu_level1+edu_level2+edu_no
            +workstatus_ft+workstatus_pt+workstatus_retired+workstatus_other, 
            data = LSOA_M)
summary(modelM_full)
```

#VIF
```{r}
library(car)
vif(modelM_full)


```
#删除：bedrooms_4more，workdistance_home，cars_2，edu_level_4more 



```{r}

#VIF处理后2
MLR_M <- lm(Mean_price_M ~ population+ bedrooms_2 + bedrooms_3 +
             workdistance_10to30 + workdistance_30more + workdistance_outside
             +centralheating_no
            +cars_3more+cars_no
            +edu_apprenticeship+edu_other+edu_level1+edu_level2+edu_no
            +workstatus_ft+workstatus_pt+workstatus_retired+workstatus_other, 
            data = LSOA_M)

# 查看模型的摘要
summary(MLR_M)

```




#线性回归
```{r}

#VIF处理后
MLR_M <- lm(Mean_price_M ~ population+ bedrooms_2 + bedrooms_3 + bedrooms_4more+
             workdistance_10to30 + workdistance_30more + workdistance_outside
             +centralheating_no
            +cars_3more+cars_no
            +edu_apprenticeship+edu_other+edu_level_1to3
            +workstatus_ft+workstatus_pt+workstatus_retired+workstatus_other, 
            data = LSOA_M)

# 查看模型的摘要
summary(MLR_M)

```

```{r}
# 安装和加载必要的包（如果尚未安装）
# install.packages("MASS") # 取消注释来安装MASS包，如果未安装

library(MASS)

# 假设data是你的数据框
# 定义全模型


# 定义基础模型
modelM_null <- lm(Mean_price_M ~ 1, data = LSOA_M)

# 进行逐步回归，direction可以是"both"（默认），"backward"或"forward"
model1_M <- step(modelM_null, scope = list(lower = modelM_null, upper = MLR_M), direction = "both")

# 查看逐步回归的结果
summary(model1_M)

```


空间滞后模型：
邻接矩阵：LSOA_knn_B
8 min


```{r}
#calculate the centroids of all Wards in London
coordsW_M <- LSOA_M%>%
  st_centroid()%>%
  st_geometry()

plot(coordsW_M)
```

Adjacency Matrix
```{r}
LSOA_nb_M <- LSOA_M %>%
  poly2nb(., queen=T)

#or nearest neighbours
knn_wards_M <-coordsW_M %>%
  knearneigh(., k=4)

LSOA_knn_M <- knn_wards_M %>%
  knn2nb()

#plot them
plot(LSOA_nb_M, st_geometry(coordsW_M), col="red")
```

```{r}
plot(LSOA_knn_M, st_geometry(coordsW_M), col="blue")
```
```{r}
#create a spatial weights matrix from these weights
Lward.lw <- LSOA_nb_M %>%
  nb2mat(., style="B")

sum(Lward.lw)
```
```{r}
sum(Lward.lw[1,])
```
```{r}
Lward.lw <- LSOA_nb_M %>%
  nb2listw(., style="C")
```

```{r}
I_LWard_Global_Density <- LSOA_M %>%
  pull(Mean_price_M) %>%
  as.vector()%>%
  moran.test(., Lward.lw)

I_LWard_Global_Density
```
#The Moran’s I statistic = 0.77 (remember 1 = clustered, 0 = no pattern, -1 = dispersed) which shows that we have some distinctive clustering

```{r}
I_LWard_Local_Density <- LSOA_M %>%
  pull(Mean_price_M) %>%
  as.vector()%>%
  localmoran(., Lward.lw)%>%
  as_tibble()

#what does the output (the localMoran object) look like?
slice_head(I_LWard_Local_Density, n=5)
```
```{r}
points_sf_joined <- LSOA_M %>%
  mutate(density_I =as.numeric(I_LWard_Local_Density$Ii))%>%
  mutate(density_Iz =as.numeric(I_LWard_Local_Density$Z.Ii))
```

```{r}
breaks1<-c(-1000,-2.58,-1.96,-1.65,1.65,1.96,2.58,1000)
```

```{r}
library(RColorBrewer)
MoranColours<- rev(brewer.pal(8, "RdGy"))
```

```{r}
tm_shape(points_sf_joined) +
    tm_polygons("density_Iz",
        style="fixed",
        breaks=breaks1,
        palette=MoranColours,
        midpoint=NA,
        title="Local Moran's I, Mean House Price in Manchester")
```

```{r}
GI_M <- 
  LSOA_M %>%
  pull(Mean_price_M) %>%
  as.vector()%>%
  globalG.test(., Lward.lw)

GI_M
```
#The General G statistic = G > expected, so high values are tending to cluster.


```{r}
# 这里是空间滞后模型22  1min
library(spatialreg)
model2_M <- lagsarlm(Mean_price_M ~population+ bedrooms_2 + bedrooms_3 +
             workdistance_10to30 + workdistance_30more + workdistance_outside
             +centralheating_no
            +cars_3more+cars_no
            +edu_apprenticeship+edu_other+edu_level1+edu_level2+edu_no
            +workstatus_ft+workstatus_pt+workstatus_retired+workstatus_other, data = LSOA_M,
               nb2listw(LSOA_knn_M, style="C"), 
               method = "eigen")



tidy(model2_M)
```


```{r}
# 这里是空间滞后模型  1min
library(spatialreg)
model2_M <- lagsarlm(Mean_price_M ~population+ bedrooms_2 + bedrooms_3 + bedrooms_4more+
             workdistance_10to30 + workdistance_30more + workdistance_outside
             +centralheating_no
            +cars_3more+cars_no
            +edu_apprenticeship+edu_other+edu_level_1to3
            +workstatus_ft+workstatus_pt+workstatus_retired+workstatus_other, data = LSOA_M,
               nb2listw(LSOA_knn_M, style="C"), 
               method = "eigen")



tidy(model2_M)
```

```{r}
# 这里是空间滞后模型2  1min
library(spatialreg)
model2_M <- lagsarlm(Mean_price_M ~population+ bedrooms_2 + bedrooms_3 +
             workdistance_10to30 + workdistance_30more + workdistance_outside
             +centralheating_no
            +cars_3more+cars_no+cars_3more
            +edu_apprenticeship+edu_other+edu_level1+edu_level2+edu_no
            +workstatus_ft+workstatus_pt+workstatus_retired+workstatus_other, data = LSOA_M,
               nb2listw(LSOA_knn_M, style="C"), 
               method = "eigen")



tidy(model2_M)
```



```{r}
glance(model2_M)
```

```{r}
summary(model2_M)
```











```{r}
AIC(model1_M, model2_M)
BIC(model1_M,model2_M)
```

```{r}
# 设置tmap绘图模式
tmap_mode("plot")

# 创建自定义颜色区间和颜色
breaks <- c(seq(0, 300000, by = 30000), Inf)
colors <- c(RColorBrewer::brewer.pal(20, "Blues"), "darkblue")

# 绘图
tm_shape(LSOA_M) +
  tm_polygons("Mean_price_M",
              breaks = breaks,
              palette = colors,
              border.col = NULL,
              title = "Mean Price of Manchester in 2021") +
  tm_layout(legend.outside = TRUE)
```


```{r}
# 确保数据已加载
# LSOA_M 和 Manchester_census 应已正确加载到你的R环境

# 使用merge函数按OutputArea合并数据
Manchester_census <- merge(Manchester_census, LSOA_M[, c("OutputArea", "Mean_price_M")], 
                            by = "OutputArea", 
                            all.x = TRUE)  # 保留Manchester_census中的所有行，即使没有匹配的OutputArea

# 检查结果
head(Manchester_census)

```

##correlation matrix

```{r}
library(corrplot) 
# 选择相关性测试的列
columns_to_test1 <- c("Mean_price_M", "population", "bedrooms_2", "bedrooms_3", "bedrooms_4more",
                      "centralheating_no",
                      "cars_2", "cars_3more","cars_no",  
                      "workstatus_pt", "workstatus_retired", "workstatus_other","workstatus_student",
                      "workdistance_10to30", "workdistance_30more", "workdistance_home", "workdistance_outside",
                      
                      "edu_level1", "edu_level2", "edu_level_4more",  "edu_no","edu_apprenticeship","edu_other"
                       )

# 计算相关矩阵
cor_matrix1 <- cor(Manchester_census[columns_to_test1], use="complete.obs")  # 排除任何NA值

# 绘制相关性矩阵图
png("corrplot1.png", width = 950, height = 950)  # 增加输出图像的尺寸
corrplot(cor_matrix1, method="color", type="upper", order="original",
         addCoef.col = "black", # 添加相关系数
         tl.col="black", tl.srt=45)  # 调整标签颜色和角度


```


```{r}
# 定义原始列名和新列名的映射
columns_to_test <- c("Mean_price_M", "population", "bedrooms_2", "bedrooms_3", "bedrooms_4more",
                     "centralheating_no", "cars_2", "cars_3more","cars_no",
                     "workstatus_pt", "workstatus_retired", "workstatus_other","workstatus_student",
                     "workdistance_10to30", "workdistance_30more", "workdistance_home", "workdistance_outside",
                     "edu_level1", "edu_level2", "edu_level_4more", "edu_no","edu_apprenticeship","edu_other")

# 确保所有列名都存在
existing_columns <- intersect(columns_to_test, colnames(Manchester_census))

# 创建新的名称映射
new_names <- c("Mean_price_M", LETTERS[1:length(existing_columns[-1])])
names(new_names) <- c("Mean_price_M", existing_columns[-1])

# 创建一个新的数据框，只包含我们想要的列，并重命名
Manchester_census_renamed <- Manchester_census[existing_columns]
colnames(Manchester_census_renamed) <- new_names[existing_columns]

# 计算相关矩阵
cor_matrix <- cor(Manchester_census_renamed, use="complete.obs")

# 绘制相关性矩阵图
png("corrplot_renamed1.png", width = 950, height = 950)
corrplot(cor_matrix, method="color", type="upper", order="original",
         addCoef.col = "black",
         tl.col="black", tl.srt=45)
dev.off()
```


##调整ing

```{r}
# FUll
modelM_1 <- lm(Mean_price_M ~ population 
            + bedrooms_4more + bedrooms_2 + bedrooms_3 
            +workdistance_home + workdistance_10to30 + workdistance_30more + workdistance_outside
            +centralheating_no
            +cars_no+cars_2+cars_3more
            +edu_apprenticeship+edu_level_4more+edu_other+edu_level1+edu_level2+edu_no
            +workstatus_pt+workstatus_retired+workstatus_other++workstatus_student, 
            data = LSOA_M)
summary(modelM_1)
```

```{r}
library(car)
vif(modelM_1)
```

```{r}
#删除eud_level_4more
modelM_1 <- lm(Mean_price_M ~ population 
            + bedrooms_4more + bedrooms_2 + bedrooms_3 
            +workdistance_home + workdistance_10to30 + workdistance_30more + workdistance_outside
            +centralheating_no
            +cars_no+cars_2+cars_3more
            +edu_apprenticeship+edu_other+edu_level1+edu_level2+edu_no
            +workstatus_pt+workstatus_retired+workstatus_other++workstatus_student, 
            data = LSOA_M)
summary(modelM_1)
```
```{r}
library(car)
vif(modelM_1)
```


```{r}
#删除cars_2
modelM_1 <- lm(Mean_price_M ~ population 
            + bedrooms_4more + bedrooms_2 + bedrooms_3 
            +workdistance_home + workdistance_10to30 + workdistance_30more + workdistance_outside
            +centralheating_no
            +cars_no+cars_3more
            +edu_apprenticeship+edu_other+edu_level1+edu_level2+edu_no
            +workstatus_pt+workstatus_retired+workstatus_other++workstatus_student, 
            data = LSOA_M)
summary(modelM_1)
```

```{r}
library(car)
vif(modelM_1)
```




```{r}
#删除p不显著的
modelM_1 <- lm(Mean_price_M ~ population 
            + bedrooms_4more  + bedrooms_3 
            +workdistance_home + workdistance_10to30 + workdistance_30more + workdistance_outside
            +centralheating_no
            +cars_no+cars_3more
            +edu_apprenticeship+edu_other+edu_level2+edu_no
            +workstatus_pt+workstatus_retired+workstatus_other++workstatus_student, 
            data = LSOA_M)
summary(modelM_1)
```

##调整

```{r}
#full
library(spatialreg)
model2_M <- lagsarlm(Mean_price_M ~population 
            + bedrooms_4more + bedrooms_2 + bedrooms_3 
            +workdistance_home + workdistance_10to30 + workdistance_30more + workdistance_outside
            +centralheating_no
            +cars_no+cars_2+cars_3more
            +edu_apprenticeship+edu_level_4more+edu_other+edu_level1+edu_level2+edu_no
            +workstatus_pt+workstatus_retired+workstatus_other+workstatus_student, data = LSOA_M,
               nb2listw(LSOA_knn_M, style="C"), 
               method = "eigen")



summary(model2_M)
```




```{r}
#删除edu_level_4more
library(spatialreg)
model2_M <- lagsarlm(Mean_price_M ~population 
            + bedrooms_4more + bedrooms_2 + bedrooms_3 
            +workdistance_home + workdistance_10to30 + workdistance_30more + workdistance_outside
            +centralheating_no
            +cars_no+cars_2+cars_3more
            +edu_apprenticeship+edu_other+edu_level1+edu_level2+edu_no
            +workstatus_pt+workstatus_retired+workstatus_other++workstatus_student, data = LSOA_M,
               nb2listw(LSOA_knn_M, style="C"), 
               method = "eigen")



summary(model2_M)
```


```{r}
#删除cars2
library(spatialreg)
model2_M <- lagsarlm(Mean_price_M ~population 
            + bedrooms_4more + bedrooms_2 + bedrooms_3 
            +workdistance_home + workdistance_10to30 + workdistance_30more + workdistance_outside
            +centralheating_no
            +cars_no+cars_3more
            +edu_apprenticeship+edu_other+edu_level1+edu_level2+edu_no
            +workstatus_pt+workstatus_retired+workstatus_other++workstatus_student, data = LSOA_M,
               nb2listw(LSOA_knn_M, style="C"), 
               method = "eigen")



summary(model2_M)
```



```{r}
#删除p不显著的1
library(spatialreg)
model2_M <- lagsarlm(Mean_price_M ~population 
            + bedrooms_4more + bedrooms_2 
            +workdistance_home + workdistance_10to30 
            +centralheating_no
            +cars_3more
            +edu_no
           +workstatus_retired+workstatus_other+workstatus_student, data = LSOA_M,
               nb2listw(LSOA_knn_M, style="C"), 
               method = "eigen")



summary(model2_M)
```

```{r}
#删除p不显著的2
library(spatialreg)
model2_M <- lagsarlm(Mean_price_M ~population 
            + bedrooms_4more + bedrooms_2 
            +workdistance_home + workdistance_10to30 
            +centralheating_no
            +cars_3more
            +edu_no
           +workstatus_retired+workstatus_student, data = LSOA_M,
               nb2listw(LSOA_knn_M, style="C"), 
               method = "eigen")



summary(model2_M)
```

```{r}
tidy(model2_M)
```


```{r}
glance(model2_M)
```

```{r}
AIC(modelM_1, model2_M)
BIC(modelM_1,model2_M)
```


```{r}
library(ggplot2)

# 假设您的数据框名为 df，并且包含 Mean_price_B 列
ggplot(LSOA_M, aes(x = Mean_price_M)) +
  geom_histogram(aes(y = ..count..), binwidth = 10000, fill = "grey", color = "black") +
  labs(title = "Distribution of Mean House Prices in Manchester",
       x = "Mean Price (£)",
       y = "Count") +
  theme_minimal() +
  scale_x_continuous(labels = scales::comma) +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
# 假设LSOA_B是您的空间数据对象
qtm(LSOA_M, fill = "Mean_price_M") +
  
  tm_compass(
    type = "8star",
    position = c("right", "bottom"),
    size = 2
  ) +
  tm_scale_bar(
    position = c("right", "bottom"),
    width = 0.15
  )
```


```{r}
# 设置tmap绘图模式
tmap_mode("plot")

# 创建自定义颜色区间和颜色
breaks <- c(seq(0, 300000, by = 50000), Inf)
colors <- c(RColorBrewer::brewer.pal(20, "Blues"), "darkblue")

# 绘图
tm_shape(LSOA_M) +
  tm_polygons("Mean_price_M",
              breaks = breaks,
              palette = colors,
              border.col = NULL,
              title = "Mean House Prices of Birmingham in 2021") +
  tm_layout(legend.outside = TRUE)
```

```{r}
tm_shape(LSOA_M) +
  tm_fill("Mean_price_M", 
          breaks = seq(0, max(LSOA_M$Mean_price_M, na.rm = TRUE) + 50000, by = 50000),
          palette = "YlOrRd",
          title = "Mean Price (£)",
          legend.format = list(text.separator = "to", fun = function(x) paste0(formatC(x, format = "f", big.mark = ",", digits = 0)))) +
  tm_borders(alpha = 0.5) +
  tm_compass(
    type = "8star",
    position = c("right", "bottom"),
    size = 2
  ) +
  tm_scale_bar(
    position = c("right", "bottom"),
    width = 0.15
  ) +
  tm_layout(
    legend.outside = TRUE,
    legend.outside.position = "right",
    frame = FALSE
  )
```



```{r}
library(ggplot2)

# 假设您的数据框名为 df，并且包含 Mean_price_B 列
ggplot(LSOA_M, aes(x = population)) +
  geom_histogram(aes(y = ..count..), binwidth = 500, fill = "grey", color = "black") +
  labs(title = "Distribution of population density in Manchester",
       x = "Population Density",
       y = "Count") +
  theme_minimal() +
  scale_x_continuous(labels = scales::comma) +
  theme(plot.title = element_text(hjust = 0.5))
```
```{r}
summary(LSOA_M$population)
```
```{r}
# 创建数据框
data <- data.frame(
  category = c("1 Car", "2 Cars", "3+ Cars", "No Car"),
  value = c(524483, 295107, 81255, 324119)
)

# 计算百分比
data$percentage <- data$value / sum(data$value) * 100

# 创建饼图
ggplot(data, aes(x = "", y = value, fill = category)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  geom_text(aes(label = sprintf("%.1f%%", percentage)), 
            position = position_stack(vjust = 0.5)) +
  labs(title = "Distribution of Car Ownership",
       fill = "Car Ownership Category") +
  theme_void() +
  theme(legend.position = "bottom",
        plot.title = element_text(hjust = 0.5, face = "bold")) +
  scale_fill_brewer(palette = "Set2")

```


```{r}
# 加载必要的包
library(ggplot2)
library(scales)

# 创建数据框
data <- data.frame(
  category = c("1 Car", "2 Cars", "3+ Cars", "No Car"),
  value = c(524483, 295107, 81255, 324119)
)

# 计算百分比
data$percentage <- data$value / sum(data$value) * 100

# 添加总数
total <- sum(data$value)

# 创建百分比堆积柱状图
ggplot(data, aes(x = "", y = percentage, fill = factor(category, levels = rev(category)))) +
  geom_bar(stat = "identity", width = 0.5) +
  geom_text(aes(label = sprintf("%.1f%%\n%s", percentage, comma(value))), 
            position = position_stack(vjust = 0.5), size = 3.5) +
  coord_flip() +  # 将图表横向显示
  labs(title = "Distribution of Car Ownership in Manchester",
       
       x = NULL,
       y = "Percentage",
       fill = "Car Ownership Category") +
  theme_minimal() +
  theme(legend.position = "right",
        plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.y = element_blank(),  # 移除y轴标签
        axis.ticks.y = element_blank()) +  # 移除y轴刻度
  scale_fill_brewer(palette = "Set2", direction = -1) +
  scale_y_continuous(labels = percent_format(scale = 1))

# 保存图表
ggsave("manchester_car_ownership.png", width = 10, height = 6, dpi = 300)

```
```{r}
# 安装并加载必要的包
if (!requireNamespace("ggplot2", quietly = TRUE)) install.packages("ggplot2")
library(ggplot2)

# 创建数据框
data <- data.frame(
  centralheating = c("Has Central Heating", "No Central Heating"),
  value = c(1207102, 17941)
)

# 计算总和和百分比
total <- sum(data$value)
data$percentage <- data$value / total * 100

# 创建堆叠柱状图
ggplot(data, aes(x = "", y = value, fill = factor(centralheating, levels = rev(centralheating)))) +
  geom_bar(stat = "identity", width = 0.5) +
  geom_text(aes(label = sprintf("%d\n(%.1f%%)", value, percentage)), 
            position = position_stack(vjust = 0.5), 
            size = 4) +
  coord_flip() +  # 将图表横向显示
  labs(title = "Distribution of Central Heating in Manchester",
       x = NULL,
       y = "Number of Households",
       fill = "Central Heating Status") +
  theme_minimal() +
  theme(legend.position = "right",
        plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.y = element_blank(),  # 移除y轴标签
        axis.ticks.y = element_blank()) +  # 移除y轴刻度
  scale_fill_manual(values = c("#66c2a5", "#fc8d62")) +  # 自定义颜色
  scale_y_continuous(labels = scales::comma)  # 使用逗号分隔数字


```

```{r}

# 创建数据框
data <- data.frame(
  bedrooms = c("1 bedroom", "2 bedrooms", "3 bedrooms", "4 + bedrooms"),
  value = c(129302, 371463, 523863, 200374)
)

# 计算总和和百分比
total <- sum(data$value)
data$percentage <- data$value / total * 100

# 创建堆叠柱状图
ggplot(data, aes(x = "", y = value, fill = factor(bedrooms, levels = rev(bedrooms)))) +
  geom_bar(stat = "identity", width = 0.5) +
  geom_text(aes(label = sprintf("%d\n(%.1f%%)", value, percentage)), 
            position = position_stack(vjust = 0.5), 
            size = 3.5) +
  coord_flip() +  # 将图表横向显示
  labs(title = "Distribution of Bedrooms in Manchester",
       x = NULL,
       y = "Number of Households",
       fill = "Number of Bedrooms") +
  theme_minimal() +
  theme(legend.position = "right",
        plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.y = element_blank(),  # 移除y轴标签
        axis.ticks.y = element_blank()) +  # 移除y轴刻度
  scale_fill_manual(values = c("#66c2a5", "#fc8d62", "#8da0cb", "#e78ac3")) +  # 自定义颜色
  scale_y_continuous(labels = scales::comma)  # 使用逗号分隔数字
```

```{r}

# Load required libraries
library(ggplot2)
library(dplyr)
library(forcats)
library(scales)  # For comma formatting of large numbers

# Create data frame for Birmingham
birmingham_work_distance <- data.frame(
  status = c("10 to 30 miles", "30+ miles", "Work from home", "Outside Birmingham", "Less than 10 miles"),
  count = c(194867, 54768, 114069, 63138, 1144955)
)

# Calculate total population
total_population <- sum(birmingham_work_distance$count)

# Add percentage column
birmingham_work_distance <- birmingham_work_distance %>%
  mutate(percentage = count / total_population * 100)

# Order work distance status by count
birmingham_work_distance <- birmingham_work_distance %>%
  mutate(status = fct_reorder(status, count))

# Lollipop chart with count and percentage labels
ggplot(birmingham_work_distance, aes(x = status, y = count)) +
  geom_segment(aes(x = status, xend = status, y = 0, yend = count), color = "skyblue") +
  geom_point(color = "darkblue", size = 4) +
  geom_text(aes(label = paste0(comma(count), "\n(", round(percentage, 1), "%)")), 
            vjust = -0.5, size = 3) +  # Add count and percentage labels
  labs(title = "Distribution of Work Distance in Birmingham",
       x = "Work Distance",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(labels = comma) +  # Use comma formatting for y-axis labels
  coord_flip()  # Flip coordinates for better readability of labels

```

```{r}
# Load required libraries
library(ggplot2)
library(dplyr)
library(forcats)
library(scales)  # For comma formatting of large numbers

# Create data frame for Manchester
manchester_work_distance <- data.frame(
  distance = c("Less than 10 km", "10 to 30 km", "30 km or more", "Work from home", "Work outside"),
  count = c(550589, 175980, 35662, 384001, 186235)
)

# Calculate percentages and order by count
manchester_work_distance <- manchester_work_distance %>%
  mutate(percentage = count / sum(count) * 100,
         distance = fct_reorder(distance, count))

# Lollipop chart with count and percentage labels
ggplot(manchester_work_distance, aes(x = distance, y = count)) +
  geom_segment(aes(x = distance, xend = distance, y = 0, yend = count), color = "skyblue") +
  geom_point(color = "darkblue", size = 4) +
  geom_text(aes(label = paste0(comma(count), "\n(", round(percentage, 1), "%)")), 
            vjust = -0.5, size = 3) +  # Add count and percentage labels
  labs(title = "Distribution of Work Distance in Manchester",
       x = "Work Distance",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(labels = comma) +  # Use comma formatting for y-axis labels
  coord_flip()  # Flip coordinates for better readability of labels
```

```{r}
# Load required libraries
library(ggplot2)
library(dplyr)
library(forcats)
library(scales)  # For comma formatting of large numbers

# Create data frame for Manchester
manchester_education <- data.frame(
  edu_level = c("Level 1", "Level 2", "Level 3", "Level 4+", "No qualifications", "Apprenticeship", "Other"),
  count = c(227767, 315673, 403047, 761762, 470159, 132738, 61946)
)

# Calculate total population and percentages
total_population <- sum(manchester_education$count)
manchester_education <- manchester_education %>%
  mutate(percentage = count / total_population * 100)

# Order education levels by count
manchester_education <- manchester_education %>%
  mutate(edu_level = fct_reorder(edu_level, count))

# Lollipop chart
ggplot(manchester_education, aes(x = edu_level, y = count)) +
  geom_segment(aes(x = edu_level, xend = edu_level, y = 0, yend = count), 
               color = "skyblue", size = 1) +
  geom_point(color = "darkblue", size = 4) +
  geom_text(aes(label = paste0(comma(count), "\n(", round(percentage, 1), "%)")), 
            vjust = -0.5, size = 3) +  # Add count and percentage labels
  labs(title = "Distribution of Education Level in Manchester",
       x = "Education Level",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(labels = comma) +  # Use comma formatting for y-axis labels
  coord_flip()
```


```{r}
library(ggspatial)
ggplot() +
  geom_sf(data = LSOA_M, aes(fill = population), color = NA) +
  scale_fill_viridis(option = "plasma", name = "Population") +
  theme_minimal() +
  labs(title = "Population Distribution in Manchester",
       subtitle = "Based on LSOA boundaries") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank()) +
  annotation_scale(location = "br", width_hint = 0.3) +
  annotation_north_arrow(location = "br", which_north = "true",
                         pad_x = unit(0.2, "in"), pad_y = unit(0.2, "in"),
                         style = north_arrow_fancy_orienteering)
```


```{r}
# Load required libraries
library(ggplot2)
library(dplyr)
library(forcats)
library(scales)  # For comma formatting of large numbers

# Create data frame for Manchester
manchester_work_status <- data.frame(
  status = c("Full-time", "Part-time", "Retired", "Other", "Student"),
  count = c(24120, 8586, 460431, 85781, 151945)
)

# Calculate total population
total_population <- sum(manchester_work_status$count)

# Add percentage column
manchester_work_status <- manchester_work_status %>%
  mutate(percentage = count / total_population * 100)

# Order work status by count
manchester_work_status <- manchester_work_status %>%
  mutate(status = fct_reorder(status, count))

# Lollipop chart with count and percentage labels
ggplot(manchester_work_status, aes(x = status, y = count)) +
  geom_segment(aes(x = status, xend = status, y = 0, yend = count), color = "skyblue") +
  geom_point(color = "darkblue", size = 4) +
  geom_text(aes(label = paste0(comma(count), "\n(", round(percentage, 1), "%)")), 
            vjust = -0.5, size = 3) +  # Add count and percentage labels
  labs(title = "Distribution of Work Status in Manchester",
       x = "Work Status",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(labels = comma) +  # Use comma formatting for y-axis labels
  coord_flip()  # Flip coordinates for better readability of labels

```
```{r}
summary(LSOA_M$Mean_price_M)
```

